\thispagestyle{empty}

\todo[inline]{adapt this statement (everything on this page)}

\section*{Declaration}
Herewith I affirm that the submitted thesis was written autonomously by
myself and that I did not use any other sources and auxiliaries than declared in
this work. Under the acknowledged rules of scientific work (lege artis) literal or
analogous content borrowed from the work of others was appropriately
identified. Furthermore, I insure that the submitted thesis is not and was
never part of any other examination procedures, either complete or in substantial
parts.

\subsection*{Declaration on the Use of Artificial Intelligence and Assistive Tools}
I hereby declare that in the preparation of this doctoral thesis, I have used Artificial
Intelligence (AI) tools as follows:

\begin{enumerate}
    \item Language and Grammar: Assistive tools (e.g., Google Gemini 3.1 Pro) were used exclusively
        to improve the linguistic quality, grammar, and formal expression of my self-generated text.
        No content was generated de novo by these tools.

    \item Image Creation

    \item Data Analysis/Coding: [If applicable] AI tools were used to support the development of
        [Python] scripts for statistical modeling. All logic and interpretations remain my own,
        and all code was manually verified for accuracy.

    \item Structuring: Generative AI was used to brainstorm section headings or outlines, which
        were subsequently reviewed, modified and filled with my original research.
\end{enumerate}

\begin{table*}[ht]
    \begin{tabularx}{\textwidth}{lXll}
        \textbf{Tool \& Version} & \textbf{Specific Task} & \textbf{Sections} & \textbf{Verification Method}\\
        \toprule
        Google Gemini 3.1 Pro & Literature research & All sections & Manual\\
    \end{tabularx}
\end{table*}

I maintain full responsibility for the accuracy, integrity, and originality of the entire work. I
confirm that all sources, including AI-assisted sections, have been transparently documented
according to the guidelines of Good Scientific Practice (GSP).

\vspace{3cm}

\hfill
\begin{tabular}[t]{c}
    \rule{17em}{0.4pt}\\Place, Date
\end{tabular}
\hfill
\begin{tabular}[t]{c}
    \rule{17em}{0.4pt}\\Signature
\end{tabular}
\hfill
